%****************************************************************************
%** Copyright 2002 by Lukas Ruf, ruf@topsy.net
%** Information is provided under the terms of the
%** GNU Free Documentation License http://www.gnu.org/copyleft/fdl.html
%** Fairness: Cite the source of information, visit http://www.topsy.net
%****************************************************************************
%** Last Modification: 2005-07-11 1600
%** 2005-07-11	Bernhard Tellenbach
%**							Inserted new content
%****************************************************************************
\clearpage
\null
\vfil % or it might be \null
\thispagestyle{plain}
\begin{center}\textbf{Abstract}\end{center}
Remote failures in the Internet can lead to minutes of connectivity loss due to the long convergence time of BGP.

Swift is a fast reroute framework designed to shorten the convergence time of a BGP speaking router. Swift predicts the cause of a failure and then reroutes traffic to unaffected peers.  

Routers connected to a industrial scale software defined Internet exchange point (iSDX), suffer like any other BGP speaking router from long convergence times upon remote failure. 

In this work we show that it is possible to integrate Swift with minor modifications into the iSDX. The convergence time of all the participants of the swifted iSDX is improved by up to a factor 60. But as both Swift and the iSDX use the destination MAC address to encode information, the amount of bits available to Swift and the iSDX is reduced. This impacts Swift's performance and the iSDX's ability to scale with a higher number of participants. The introduced overhead by Swift to process a single BGP update is minimal. 
\vfil
\clearpage 
