%****************************************************************************
%** Copyright 2002 by Lukas Ruf, ruf@topsy.net
%** Information is provided under the terms of the
%** GNU Free Documentation License http://www.gnu.org/copyleft/fdl.html
%** Fairness: Cite the source of information, visit http://www.topsy.net
%****************************************************************************

%Example structure for an introduction
%****************************************************************************
%** Copyright 2002, 2003 by Lukas Ruf, <ruf@topsy.net>
%** Information is provided under the terms of the
%** GNU Free Documentation License <http://www.gnu.org/copyleft/fdl.html>
%** Fairness: Cite the source of information, visit <http://www.topsy.net>
%****************************************************************************

\chapter{\label{introduction}Introduction}
The border gateway protocol (BGP) is the glue that holds the Internet together by allowing 
autonomous networks to exchange information about the reachability of prefixes without revealing their own network infrastructure. 

Remote disruptions in BGP can lead to convergence times of multiple minutes. This long convergence time is caused by the way BGP updates are propagated through the Internet. The convergence time is lower bounded by the time it takes for all BGP withdrawal updates to be received. Standard BGP routers have to update the data plane on a per prefix basis. The router has converged once the last withdrawal has been received and processed. Swift is a fast reroute and prediction framework that can be deployed at a BGP router. It predicts the cause of the remote disruption and fast reroutes traffic, thus shortening the convergence time significantly. Swift is based on software defined networking. 

Software defined networking (SDN) allows network operators to have more control over the network, by abstracting lower level functionality and making control directly programmable. The industrial scale Internet exchange point (iSDX) makes use of SDN technology to give participants more control over the traffic at the exchange point. 

In this project we show that it is possible to improve the convergence time at software defined exchange points, such as the iSDX using the Swift framework. As both the iSDX and Swift rely on a similar infrastructure to enable their functionality, it is intuitive to integrate Swift into the iSDX. 

In the following, We will first provide some background on BGP, iSDX and Swift in chapter \ref{chapter2}. Then we describe the motivation behind implementing Swift in the iSDX in chapter \ref{chapter3}. In chapter \ref{chapter4} we present the design of the iSDX with Swift. In chapter \ref{chapter5} we evaluate the system both in terms of convergence time and introduced overhead and discuss the results in chapter \ref{chapter6}. 



